Skills, Practices, and Aspirations \\ of Small-scale Entrepreneurs \\ in Low-income Settings

### 2021-02-09 firms/mgmt/MSMEmgmt_Bocconi_03-2021.tex
Many small tweaks
Added eq and colors

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\vspace{0.1in}
	\end{itemize_2pt}
\end{frame}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
	\label{McKenzie(2017): Hetereogeneity}
\end{figure}

>>>>

\begin{frame}
\frametitle{Heterogeneity in Business Practices}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2010): Heterogeneity \citep{Bloom2010}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices and Performance}
	\begin{itemize_2pt}
	\item Bloom and van Reenen (2019): Correlation with productivity \citep{Bloom2019}
	\end{itemize_2pt}
\end{frame}

\begin{frame}
\frametitle{Business Practices in the Production Decision}

Standard Production Decision
	\begin{itemize_2pt}
		\item Owner maximizes output $Y = f(A, L, M, K)$ at given wealth $W$:

		\item[] $\boxed{\begin{aligned} \max _{K, M, L} &\{\textcolor{red}{p} &\ f(\textcolor{red}{A}, \textcolor{bdf}{L, M, K})-\textcolor{red}{w} \textcolor{bdf}{L}-\textcolor{red}{s} \textcolor{bdf}{M}-\textcolor{red}{r} \textcolor{bdf}{K}\} \end{aligned}}$
		\item[] $\begin{aligned} \text{s.t.} &\ \textcolor{red}{w} \textcolor{bdf}{L}+\textcolor{red}{s} \textcolor{bdf}{M}+\textcolor{red}{r} \textcolor{bdf}{K} \leq \lambda W \end{aligned}$

		\begin{itemize_2pt}
			\item[] .. where $\textcolor{bdf}{L}$ is labor, $\textcolor{bdf}{M}$ is materials, and $\textcolor{bdf}{K}$ is capital.
			\item[] .. where $\textcolor{red}{p}$ is the output price, $\textcolor{red}{w}$ the cost of labor, $\textcolor{red}{s}$ the cost of raw materials, $\textcolor{red}{r}$ cost of capital, and $\textcolor{red}{A}$ 							represents a productivity factor.
		\end{itemize_2pt}
	%\item Bloom et al. (2016) Bloom N, Sadun R, Van Reenen J (2016) Management as a technol- ogy? NBERWorking Paper 22327, National Bureau of Economic Research, Cambridge, MA.
	%\item McKenzie2017 3.1.
	\end{itemize_2pt}

@@

\begin{figure}[htbp]
	\centering
	\includegraphics[width=23em]{pics/McKenzie2017_het.png}
	\label{McKenzie(2017): Heterogeneity}
\end{figure}
